---
title: "Assignment 3"
author: "Kaili Brande, Bridget Gibbons"
date: "4/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading in necessary packages, the data, and the updated yield model

```{r}


library(ggplot2)
library(pse)
library(sensitivity)
library(tidyverse)


clim = data.frame(read_csv("clim.csv"))

```

```{r}

# Adjust your almond model to  output ONLY the mean almond yield anomoly IF the users sets parameter (e.g mean_only = TRUE))

source("yield_function_assignment3.R")

yield_function_assignment3(climate = clim)

```

## Performing a sensitivity analysis of how mean anomaly varies ALL of the parameters used in the yield model 

```{r}

# Assuming parameters are normally distributed with standard deviation of 20% mean value


```

## Rank the parameters in term of their sensitivity

```{r}

```

## Graph uncertainty in mean yield anomaly across all parameter uncertainty (boxplot and cummulative distribution of the output).

```{r}


```

## Repeat using the LHS method:

```{r}

```

## Repeat using the Sobol method:

```{r}

```

## Repeat using twice as many parameter sets as you did in your first sensitivity analysis, to evaluate how this changes the sensitivity results

```{r}

```

## 