---
title: "Assignment 3"
author: "Kaili Brande, Bridget Gibbons"
date: "4/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## Loading in necessary packages, the data, and the updated yield model

```{r}


library(ggplot2)
library(pse)
library(sensitivity)
library(tidyverse)


clim = data.frame(read_csv("clim.csv"))

```

```{r}

# Adjust your almond model to  output ONLY the mean almond yield anomoly IF the users sets parameter (e.g mean_only = TRUE))

source("yield_function_assignment3.R")


```

## Performing a sensitivity analysis of how mean anomaly varies ALL of the parameters used in the yield model 

### Using the LHS method:

```{r}

# Assuming parameters are normally distributed with standard deviation of 20% mean value

# First defining the range of input parameters

factors = c("x1", "x2", "x3", "x4", "intercept")

# Deciding how many parameter sets to run

nsets = 100

# Indicating which distribution

q = c("qnorm", "qnorm", "qnorm", "qnorm", "qnorm")

# Defining arguments

### standard deviation is 0.20 * mean (the value of the parameter in the function)

sd_x1 = abs(0.20 * -0.015)
sd_x2 = abs(0.20 * -0.0046)
sd_x3 = abs(0.20 * -0.07)
sd_x4 = abs(0.20 * 0.0043)
sd_intercept = abs(0.20 * 0.28)

q.arg = list(list(mean = -0.015, sd = sd_x1), list(mean = -0.0046, sd = sd_x2), list(mean = -0.07, sd = sd_x3), list(mean = 0.0043, sd = sd_x4), list(mean = 0.28, sd = sd_intercept))

# Generating the samples

y = LHS(NULL, factors, nsets, q, q.arg)
LHS_pars = get.data(y)
head(LHS_pars)

# Creating a data frame to store the results when we run the model

LHS_results = matrix(nrow=nsets, ncol= 5)

# Now running the model over these parameter sets
### We will use the faster way, using mapply (versus for loop)

LHS_model_results = mapply(FUN=yield_function_assignment3, x1=LHS_pars$x1, x2=LHS_pars$x2, x3=LHS_pars$x3, x4=LHS_pars$x4, intercept=LHS_pars$intercept,  MoreArgs=list(clim=clim))

# Putting the results in our previously created matrix

LHS_results = matrix((unlist(LHS_model_results)), ncol= 5, byrow=TRUE)

### Assigning column names

colnames(LHS_results)=c("x1","x2", "x3", "x4", "intercept")

```

### Ranking the parameters in term of their sensitivity

```{r}

# using plotprcc to graph and using the prcc column of the data frame to determine the ranks

y = pse::tell(y, t(LHS_results), res.names=c("x1","x2", "x3", "x4", "intercept"))

pse::plotprcc(y)
y$prcc

## From the PRCC graphs, we can see that the rank of the parameters (from largest to smallest) are: intercept, x4, x2, x3, and x1.

```

### Graphing uncertainty in mean yield anomaly across all parameter uncertainty (boxplot and cumulative distribution of the output)

```{r}

# using plotscatter

pse::plotscatter(y, col="blue", cex=5)

# ggplot and geom_boxplot()

LHS_results = as.data.frame(LHS_results)
ggplot(LHS_results, aes(x1, x2, x3, x4, intercept))+geom_point()+labs(y="x1", "x2", "x3", "x4", "intercept")

# now need to add uncertainty bounds on our estimates


LHS_results = LHS_results %>% gather(value="mean_value", key="yield")

ggplot(LHS_results, aes(yield, mean_value, col=yield))+geom_boxplot()+labs(y="Yield (as Anomaly)")

ggplot(LHS_results, aes(yield, mean_value, col=yield))+geom_boxplot()+labs(y="Yield (as Anomaly)")+facet_wrap(~yield, scales="free")

```


## Using the Sobol method:

```{r}

# sobol method - short

# number of parameters
np = 500

# distributions for parameters

sobol_x1 = rnorm(mean = -0.015, sd = 0.003, n = np)
sobol_x2 = rnorm(mean = -0.0046, sd = 0.00092, n = np)
sobol_x3 = rnorm(mean = -0.07, sd = 0.014, n = np)
sobol_x4 = rnorm(mean = 0.0043, sd = 0.00086, n = np)
sobol_int = rnorm(mean = 0.28, sd = 0.056, n = np)

X1 = cbind.data.frame(sobol_x1, sobol_x2, sobol_x3, sobol_x4, sobol_int)

# repeate distribution sampling

sobol_x1 = rnorm(mean = -0.015, sd = 0.003, n = np)
sobol_x2 = rnorm(mean = -0.0046, sd = 0.00092, n = np)
sobol_x3 = rnorm(mean = -0.07, sd = 0.014, n = np)
sobol_x4 = rnorm(mean = 0.0043, sd = 0.00086, n = np)
sobol_int_5 = rnorm(mean = 0.28, sd = 0.056, n = np)

X2 = cbind.data.frame(sobol_x1, sobol_x2, sobol_x3, sobol_x4, sobol_int_5)

sens_yield_sobol_short = sobol2007(model = NULL, X1, X2, nboot = 100)

# run model for the parameter sets

sobol_result = mapply(FUN = yield_function_assignment3, 
                      x1 = sens_yield_sobol_short$X$sobol_x1, 
                      x2 = sens_yield_sobol_short$X$sobol_x2, 
                      x3 = sens_yield_sobol_short$X$sobol_x3, 
                      x4 = sens_yield_sobol_short$X$sobol_x4, 
                      intercept = sens_yield_sobol_short$X$sobol_int_5, 
                      MoreArgs = list(climate = clim))

sobol_short_tell = sensitivity::tell(sens_yield_sobol_short, sobol_result, sobol_result.names="mean_value")

sobol_short_tell$S

sobol_short_tell$T

#print(sobol_short_tell)
plot(sobol_short_tell)

```

### Ranking the parameters in term of their sensitivity

```{r}

order(sobol_short_tell$S$original)

```

### Graphing uncertainty in mean yield anomaly across all parameter uncertainty (boxplot and cumulative distribution of the output)

```{r}

s_short_result <- matrix((unlist(sobol_result)), ncol = 1, byrow = TRUE)
colnames(s_short_result) = c("mean_value")

s_short_result_df <- as.data.frame(s_short_result)

s_short_result_2 <- cbind.data.frame(sobol_short_tell$X, mean_value = sobol_short_tell$y)

s_short_result_box <- gather(s_short_result_2, key = "parameter", value = "values", sobol_x1, sobol_x2, sobol_x3, sobol_x4, sobol_int)
  
# boxplot

ggplot(data = s_short_result_df, aes(x = "", y = mean_value)) +
    geom_boxplot() +
    labs( 
     title = "Sobol-Short Uncertainty",
      x = "Almond",
      y = "Yield (as anomoly)"
      ) +
    theme_classic()

boxplot2 <- ggplot(data = s_short_result_box, aes(x = parameter, y = values)) +
    geom_boxplot() +
    labs( 
     title = "Sobol-Short Parameter Effects",
      x = "Almond",
      y = "Yield (as anomoly)"
      ) +
    theme_classic()

boxplot2

# cumulative distribution

ggplot(s_short_result_df, aes(mean_value)) +
  stat_ecdf(geom = "step") +
  xlab("Mean Yield Anomaly (ton/acre)") +
  labs(title = "Cumulative Distribution Sobol-Short Method") +
  theme_classic()


```

# Now we can compare the LHS and Sobol graphs

```{r}

#ggplot(LHS_results, aes(yield, mean_value, col=yield)) + geom_boxplot() + geom_boxplot(sobol results) + labs(y="Yield (as Anomaly)")


```

## Repeating both methods using twice as many parameter sets as you did in your first sensitivity analysis, to evaluate how this changes the sensitivity results

###LHS Method:

```{r}

# For LHS method
nsets_2 = 2 * 100

y_2 = LHS(NULL, factors, nsets_2, q, q.arg)
LHS_pars_2 = get.data(y_2)
head(LHS_pars_2)

# Creating a data frame to store the results when we run the model

LHS_results_2 = matrix(nrow=nsets_2, ncol= 5)

# Now running the model over these parameter sets
### We will use the faster way, using mapply (versus for loop)

LHS_model_results_2 = mapply(FUN=yield_function_assignment3, x1=LHS_pars_2$x1, x2=LHS_pars_2$x2, x3=LHS_pars_2$x3, x4=LHS_pars_2$x4, intercept=LHS_pars_2$intercept,  MoreArgs=list(clim=clim))

# Putting the results in our previously created matrix

LHS_results_2 = matrix((unlist(LHS_model_results_2)), ncol= 5, byrow=TRUE)

### Assigning column names

colnames(LHS_results_2)=c("x1","x2", "x3", "x4", "intercept")


# ranking the parameters
y_2 = pse::tell(y_2, t(LHS_results_2), res.names=c("x1","x2", "x3", "x4", "intercept"))

pse::plotprcc(y_2)
y_2$prcc

# now graphing

LHS_results_2 = LHS_results_2 %>% gather(value="mean_value", key="yield")

ggplot(LHS_results_2, aes(yield, mean_value, col=yield))+geom_boxplot()+labs(y="Yield (as Anomaly)")

# and comparing these secondary results to the first LHS analysis (where we hadn't doubled nsets)

ggplot(LHS_results_2, aes(yield, mean_value, col=yield))+geom_boxplot()+ geom_boxplot(LHS_results) + labs(y="Yield (as Anomaly)")


```

### Sobol Method

```{r}

# sobol method - long

# number of parameters
np = 1000

# distributions for parameters

sobol_x1 = rnorm(mean = -0.015, sd = 0.003, n = np)
sobol_x2 = rnorm(mean = -0.0046, sd = 0.00092, n = np)
sobol_x3 = rnorm(mean = -0.07, sd = 0.014, n = np)
sobol_x4 = rnorm(mean = 0.0043, sd = 0.00086, n = np)
sobol_int_5 = rnorm(mean = 0.28, sd = 0.056, n = np)

X1 = cbind.data.frame(sobol_x1, sobol_x2, sobol_x3, sobol_x4, sobol_int_5)

# repeate distribution sampling

sobol_x1 = rnorm(mean = -0.015, sd = 0.003, n = np)
sobol_x2 = rnorm(mean = -0.0046, sd = 0.00092, n = np)
sobol_x3 = rnorm(mean = -0.07, sd = 0.014, n = np)
sobol_x4 = rnorm(mean = 0.0043, sd = 0.00086, n = np)
sobol_int = rnorm(mean = 0.28, sd = 0.056, n = np)

X2 = cbind.data.frame(sobol_x1, sobol_x2, sobol_x3, sobol_x4, sobol_int_5)

sens_yield_sobol_long = sobol2007(model = NULL, X1, X2, nboot = 100)

# run model for the parameter sets

sobol_result = mapply(FUN = yield_function_assignment3, 
                      x1 = sens_yield_sobol_long$X$sobol_x1, 
                      x2 = sens_yield_sobol_long$X$sobol_x2, 
                      x3 = sens_yield_sobol_long$X$sobol_x3, 
                      x4 = sens_yield_sobol_long$X$sobol_x4, 
                      intercept = sens_yield_sobol_long$X$sobol_int_t, 
                      MoreArgs = list(climate = clim))

sobol_long_tell = sensitivity::tell(sens_yield_sobol_long, sobol_result, sobol_result.names="mean_value")

#sobol_long_tell$S

#sobol_long_tell$T

print(sobol_long_tell)
plot(sobol_long_tell)

# parameter effect

order(sobol_long_tell$S$original)

# sobol - long plots

s_long_result <- matrix((unlist(sobol_result)), ncol = 1, byrow = TRUE)
colnames(s_long_result) = c("mean_value")

s_long_result_df <- as.data.frame(s_long_result)

# boxplot

ggplot(data = s_long_result_df, aes(x = " ", y = mean_value)) +
    geom_boxplot() +
    labs( 
     title = "Sobol-Long Uncertainty",
      x = "Almond",
      y = "Yield (as anomoly)"
      ) +
    theme_classic()

# cumulative distribution

ggplot(s_long_result_df, aes(mean_value)) +
  stat_ecdf(geom = "step") +
  xlab("Mean Yield Anomaly (ton/acre)") +
  labs(title = "Cumulative Distribution Sobol-Long Method") +
  theme_classic()

```
 
 ## Comparing the short and long versions for each method:
 
 ### LHS
 
```{r}

```
 
 
 ### Sobol
 
```{r}

# boxplot

ggplot() +
  geom_boxplot(data = s_short_result_df, aes(x = " ", y = mean_value), fill = "blue") +
  geom_boxplot(data = s_long_result_df, aes(x = " ", y = mean_value), fill = "green") +
  theme_classic() +
  labs( 
     title = "Sobol-Long Uncertainty",
      x = "Almond",
      y = "Yield (as anomoly)"
      )

  

# cumulative distribution

ggplot() +
  stat_ecdf(geom = "step", data = s_short_result_df, aes(mean_value), color = "blue") +
  stat_ecdf(geom = "step", data = s_long_result_df, aes(mean_value), color = "green") +
  theme_classic() +
  labs( 
     title = "Sobol Method - Cumulative Distribution",
     x = "Mean Yield Anomaly (ton/acre)",
     y = "Cululative Distribution"
      )


```
 
 