---
title: "climate_crop_model"
author: "Bridget Gibbons"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading in the climate data provided (clim.txt): 

```{r}

library(tidyverse)
clim = data.frame(read_csv("clim.csv"))
view(clim)


clim_month = clim %>% 
  group_by(month, year) %>% 
  summarize(meantmax = mean(tmax_c), precip=sum(precip)) 

## gives average monthly maximum daily temperature, and monthly precipitation from a data frame called clim  with columns year, month, precip and tmax_c


## Filtering the data frame for only months 1 and 2. This is because our min daily temperature must be in month 2 and our precipitation must be in month 1.

clim_month_1and2 = clim_month %>%
filter(month %in% c(1, 2))


```

# Bringing in our model from our .R file:

```{r}

source("")

```

# 3. 
## Using our model to estimate how almond yield anomalies for each year in the record:

```{r}



```


## Graphing the results:

```{r}



```


# 4.
## Estimating the mean annual yield anomaly if the last 20 years had been 2C warmer:

```{r}



```

# 5.
## Varying one of the parameters by sampling from a normal distribution; with mean the value from Lobell et al., (2006) and standard deviation 10% of the mean

```{r}



```

## Creating a box plot of mean annual yield anomaly for baseline and 2C climate (boxes show variation due to uncertainty in the parameter):

```{r}



```
